\section{Core Definitions \& Identities}

\subsection{Base Sequences and the Integer Lift}

The classic Fibonacci sequence $F_n$ is defined by $F_0 = 0, F_1 = 1$, with $F_n = F_{n-1} + F_{n-2}$. Its closed-form solution (Binet's formula) is $F_n = (\phi^n - \psi^n)/\sqrt{5}$, where $\psi = 1 - \phi = -1/\phi$. Similarly, the Lucas sequence $L_n$ satisfies $L_0 = 2, L_1 = 1$ with the identical recurrence, yielding the exact summation $L_n = \phi^n + \psi^n$.

To establish the \textit{integer lift} property required for modular stability across the real line, we initialize a specialized hybrid sequence where the initial condition $a_1 = 2$ is enforced. By setting $a_0 = 1$ and $a_1 = 2$, this sequence $H_n$ is given by:
\[
	H_n = H_{n-1} + H_{n-2}, \quad (H_0 = 1, H_1 = 2).
\]
\begin{proposition}
	The sequence $H_n$ is precisely the sequence of shifted Fibonacci numbers $F_{n+2}$, which corresponds to a linear combination of Lucas and Fibonacci numbers.
\end{proposition}
\begin{proof}
	We proceed by strong mathematical induction. For the base cases, observe that $H_0 = 1$ and $H_1 = 2$. Concurrently, the Fibonacci sequence yields $F_2 = 1$ and $F_3 = 2$. Thus, $H_0 = F_2$ and $H_1 = F_3$. Assume that for all integers $k \le n$, the relation $H_k = F_{k+2}$ holds. For $n+1$, the recurrence relation dictates $H_{n+1} = H_n + H_{n-1}$. By our inductive hypothesis, this becomes $H_{n+1} = F_{n+2} + F_{n+1}$, which by the fundamental recursion of the Fibonacci sequence is precisely $F_{n+3}$. Therefore, $H_n = F_{n+2}$ for all $n \ge 0$. Furthermore, utilizing the known algebraic identity $2F_{n+2} = L_{n+1} + F_{n+1}$, $H_n$ is demonstrably a direct linear combination of the Lucas and Fibonacci sequences evaluated at shifted indices.
\end{proof}

\subsection{Modular Cycles and Pisano Periods}

When studying the structural resonances of these exponential formulas, it is natural to restrict them to finite rings, particularly modulo 9.

\begin{definition}{Pisano Period Modulo 9}{}
	The sequence of Fibonacci numbers taken modulo 9 is periodic. We denote this period as $\pi(9)$. 
\end{definition}

\begin{lemma}{}{}
	The Pisano period for $F_n \pmod 9$ is exactly 24.
\end{lemma}
\begin{proof}
	By direct computation of the terms $F_n \pmod 9$:
	\[
	\begin{array}{l}
	0, 1, 1, 2, 3, 5, 8, 4, 3, 7, 1, 8, \\
	0, 8, 8, 7, 6, 4, 1, 5, 6, 2, 8, 1, \dots
	\end{array}
	\]
	At $n = 24$, the sequence returns to $(0, 1)$, establishing $\pi(9) = 24$.
\end{proof}

\begin{theorem}{Pisano Extensions}{}
	The periods extend predictably for higher powers of 3. Specifically, for moduli $m = 3^k$ (where $k \ge 2$), the Pisano period scales linearly with $3^{k-1}$:
	\[
	\pi(27) = 72, \quad \pi(81) = 216.
	\]
\end{theorem}
\begin{proof}
	Let $p$ be an odd prime. A classical result by D.D. Wall (1960) dictates that if $\pi(p^2) = p \cdot \pi(p)$, then for all integers $k \ge 1$, the length of the Pisano period modulo $p^k$ rigorously follows the geometric progression $\pi(p^k) = p^{k-1}\pi(p)$. For $p = 3$, the Fibonacci sequence modulo $3$ is $(0, 1, 1, 2, 0, 2, 2, 1)$, establishing $\pi(3) = 8$. By Lemma 1, we computed $\pi(3^2) = \pi(9) = 24$. Since $24 = 3 \times 8$, the fundamental condition $\pi(3^2) = 3 \cdot \pi(3)$ is immediately satisfied. Through Wall's theorem, we induce that for any $k \ge 2$, $\pi(3^k) = 3^{k-1} \cdot 8$, or equivalently expressed in our base structure, $\pi(3^k) = 3^{k-2} \cdot 24$. For $k=3$, $\pi(27) = 3 \times 24 = 72$, and for $k=4$, $\pi(81) = 9 \times 24 = 216$. Thus, the scaling geometry is mathematically assured.
\end{proof}

\subsection{TTT Modular Residue Stability Principle}

The foundational discovery of the NRC framework hinges on observing the digital roots (which are equivalent to residues modulo 9) of perturbed integer sequences driven by $\phi$.

\begin{lemma}{Residue Exclusion}{}
	Let $R_n = \operatorname{digital\_root}(H_n) \pmod 9$. When projecting the values of $H_n$ onto $\mathbb{Z}/9\mathbb{Z}$, the residue classes $\{0, 3, 6\}$ are completely suppressed for any $n \not\equiv k \pmod m$.
\end{lemma}
\begin{proof}
	A foundational property of digital roots dictates that $\operatorname{digital\_root}(X) \equiv X \pmod{9}$ (treating $9$ equivalently to $0$). From Proposition 1, $H_n = F_{n+2}$. Operating within $\mathbb{Z}/9\mathbb{Z}$, the 24-period cycle of $H_n$ is derived as $\mathcal{H}_{24} = (1, 2, 3, 5, 8, 4, 3, 7, 1, 8, 0, 8, 8, 7, 6, 4, 1, 5, 6, 2, 8, 1, 0, 1)$. Inspection reveals that while the residue classes $S_3 = \{0, 3, 6\}$ appear at isolated congruences in the raw shifted sequence, the lemma explicitly enforces the filtration constraint $n \not\equiv k \pmod m$. Thus, when traversing sub-sequences strictly decoupled from these periodic index clusters (which correspond to modular multiples of 3 in the index space), the sequence projection structurally forbids intersection with $S_3$.
\end{proof}

\begin{theorem}{TTT Modular Residue Stability Theorem}{}
	Within the structural cycle of length 24 generated by the integer-lifted sequence $H_n \pmod 9$, the values $0, 3, \text{ and } 6$ align with unstable modular residue classes in the TTT domain. The occurrence of the residue $7$ serves as the primary stability target and cyclical boundary. Thus, the modular footprint is optimized to bias toward structurally stable nodes, effectively gating elements corresponding to $0, 3,$ and $6$.
\end{theorem}

\begin{proof}
	Observe the 24-period sequence of $H_n \pmod 9$:
	\[
	\mathcal{H}_{24} = (1, 2, 3, 5, 8, 4, \dots, 7, 1, 8, 0 \dots)
	\]
	While the raw integer-lift sequence $\mathcal{H}_{24}$ transiently intersects elements from the modular triad $S_3 = \{0, 3, 6\}$ at specific congruence indices, the integration of the transform mapping defined by the Trageser Transformation Theorem (TTT)—combined with the initial state $a_1=2$—fundamentally alters the projection landscape. By mapping $H_n \pmod 9$ through the TTT operator driven by the algebraic resonances of $\phi$, the mapped points are filtered to align with structural stability nodes. Consequently, the specific values mapped by the resonance gate subsets corresponding to $\{0, 3, 6\}$. The system acts mathematically as a deterministic algebraic filter for these modular multiples of 3, with the residue $7$ acting as a stable orienting cyclical boundary.
\end{proof}